Basic Model formulation

### 2015-04-14 documentation/model_formulation.Rmd
update attractant-decoy and associational resistance

parms <- defparms
parms$f = 0.8
parms$b = 0.3

@@

parms <- defparms
parms$v = 0.9
attractor(parms, pairapprox = FALSE, meanfield = FALSE, localvals = TRUE)

@@

**Update 12.03.2015:** since the effect is of less relevance at high cover, since the development of thorns is only induced if local pressure is already high,  it makes more sense to implement associational protection as an effect on search efficiency.

@@

This causes a to fall to its minimal value ($1-p$) at full local cover.

@@

parms <- defparms
parms$p = 0.8
attractor(parms, pairapprox = FALSE, meanfield = FALSE, localvals = TRUE)

@@

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = r \rho_1^{1+\alpha} (b + (1 - b)  f \rho_1)) (1-\frac{\rho_1}{K(1 - c \rho_1}) - \rho_{1}m - \frac{(a  + v \rho_1)L (1 - p \rho_1)\rho_1^{1+q}}{1+(a  + v \rho_1)h\rho_1^{1+q}}  $$

@@

$$ C = \rho_{1}m + \frac{(a  + v \rho_1)L (1 - p \rho_1)\rho_1^{1+q}}{1+(a  + v \rho_1)h\rho_1^{1+q}}$$

>>>>

defparms <- list(  
    m = 0.05,
    r = 1,
    b = 0.9, 
    K = 0.9, 
    a = 0.6,
    h = 100,
    L = 12, 
    alpha = 0,
    q = 0,
    c = 0,
    f = 0,
    v = 0,
    p = 0

  )
parms <- defparms
parms$f = 0.8
parms$b = 0.3

@@

parms <- defparms
parms$v = 1
parms$q = 1
attractor(parms, pairapprox = FALSE, meanfield = FALSE, localvals = TRUE)

@@

**Update 12.03.2015:** the effect is of less relevance at high cover, since the development of thorns is only induced if local pressure is already high. At high cover it is the handling time limitation that acts as an individual protection. Thus, it makes more sense to implement associational protection as an effect on search efficiency.

@@

This causes $a$ to fall to its minimal value ($1-p$) at full local cover. If $p=1$ the feeding is completely neutralized under high local cover, which also causes a drop in grazing mortality if cover is really high. This might be unrealistic, for the biological reasons named above. So, values of $p \leq 0.9$ seem to make sense.

**Update 26.03.2015:** Also, the formulations of local effects on mortality are unclear about their compatibility, since the attractant effect it is additive while the protective effect is multiplied. 
Thus, I have to specify

$$ a =  (a^*  + v q_{1|1} ) (1- p q_{1|1}) $$

@@

parms <- defparms
parms$p = 0.99
attractor(parms, pairapprox = FALSE, meanfield = FALSE, localvals = TRUE)

@@

$$  \frac{\mathrm{d}\rho_{1}}{\mathrm{d}t} = r \rho_1^{1+\alpha} (b + (1 - b)  f \rho_1)) (1-\frac{\rho_1}{K(1 - c \rho_1}) - \rho_{1}m - \frac{(a  + v \rho_1)(1 - p \rho_1)L \rho_1^{1+q}}{1+(a  + v \rho_1)h\rho_1^{1+q}}  $$

@@

$$ C = \rho_{1}m + \frac{(a  + v \rho_1)(1 - p \rho_1)L \rho_1^{1+q}}{1+(a  + v \rho_1)h\rho_1^{1+q}}$$
